Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-21 paper_comparison/appendix.Rmd
add number of eval plot

```{r conv-x-dist, fig.cap = "Change of power of conventional tests under different fitted value distribution for non-linearity model and heteroskedasticity model.", fig.height = 4}
bind_rows(poly_x_dist, heter_x_dist) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +

@@

@@

>>>>

```{r conv-x-dist, fig.cap = "Change of power of conventional tests under different fitted value distribution for non-linearity model and heteroskedasticity model.", fig.height = 3}
bind_rows(poly_x_dist, heter_x_dist) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +

@@

```{r}
eval_n <- function(n_eval, boot) {
  map_df(1:boot, function(boot_id) {
  vi_survey %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  filter(x_dist == "uniform") %>%
  filter(type == "polynomial") %>%
  group_by(unique_lineup_id) %>%
  slice_sample(n = n_eval) %>%
  ungroup() %>%
  calc_p_value_multi(lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha) %>%
  mutate(boot_id = boot_id)
}) %>%
  left_join(select(vi_survey, unique_lineup_id, effect_size)) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  select(-unique_lineup_id, -p_value) %>%
  mutate(n_eval = n_eval)
}

map_df(seq(1, 11, 2), ~eval_n(.x, 1)) %>%
  select(-boot_id) %>%
  nest(c(effect_size, reject, offset0)) %>%
  mutate(mod = map(data, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-data, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  ggplot() +
  geom_line(aes(log_effect_size, power, col = factor(n_eval)),
            size = 1) +
  theme_light() +
  scale_color_brewer(palette = "PuBuGn")
```

@@

```{r}

```
